Measurement of a dwarf galaxy rotational velocity from its Lyman-alpha line emission

### 2015-09-23 paper/letter.tex
small changes

\newcommand{\tol}{TOL1214-277}
\newcommand{\hb}{H$\beta$}
\newcommand{\ha}{H$\alpha$}
\newcommand{\oiii}{[OIII]}
\newcommand{\oii}{[OII]}
\newcommand{\nii}{[NII]}
\newcommand{\esca}{erg cm$^{-2}$ s$^{-1}$ \AA$^{-1}$}
\newcommand{\esc}{erg cm$^{-2}$ s$^{-1}$}
\newcommand{\es}{erg s$^{-1}$}
\newcommand{\esa}{erg s$^{-1}$}
\newcommand{\kms}{km s$^{-1}$}
\def\simgt{\lower.5ex\hbox{\gtsima}}
\def\simlt{\lower.5ex\hbox{\ltsima}}
%------------------------------------------------------

@@

Figure 1. shows the observational data for \tol with the overplot from
our best fit model. The parameters for the best fit are
$v_{max}=300$kms, $\tau=1\times10^7$, $T=1.5\times 10^{4}$K and a
viewing angle $\theta<30$ degrees.

@@

We estimate the total neutral hydrogen mass to be $M\approx
m_H\tau^3\sigma^{-3}n^{-2}$, where $m_H$ is the mass a Hydrogen's atom, $\tau$ is
the optical depth, $\sigma$ is the cross section at the line's center
and $n$ is the number density of neutral Hydrogen atoms. For this
system we estimate that for average values of $n=1\times 10^3$ the
total hydrogen mass is $M\times 10^{14}$M$_{\odot}$. However, blind HI
surveys have put an upper limit in the neutral hydrogen mass of ???

>>>>

\newcommand{\tol}{TOL1214-277}
\newcommand{\lya}{Ly$\alpha$}
\newcommand{\hb}{H$\beta$}
\newcommand{\ha}{H$\alpha$}
\newcommand{\oiii}{[OIII]}
\newcommand{\oii}{[OII]}
\newcommand{\nii}{[NII]}
\newcommand{\esca}{erg cm$^{-2}$ s$^{-1}$ \AA$^{-1}$}
\newcommand{\esc}{erg cm$^{-2}$ s$^{-1}$}
\newcommand{\es}{erg s$^{-1}$}
\newcommand{\esa}{erg s$^{-1}$}
\newcommand{\kms}{km s$^{-1}$}
\def\simgt{\lower.5ex\hbox{\gtsima}}
\def\simlt{\lower.5ex\hbox{\ltsima}}
%------------------------------------------------------

@@

Figure 1. shows the observational data for \tol with the overplot from
our best fit model from the full radiative transfer simulation. 
The parameters for the best fit are
$v_{max}=300$\kms, $\tau=1\times10^7$, $T=1.5\times 10^{4}$K and a
viewing angle $\theta<30$ degrees.

@@

Assuming spherical symmetry and a homogeneous gas distribution we
estimate the total neutral hydrogen mass to be on the order of
$M\approx m_H\tau^3\sigma^{-3}n^{-2}$, where $m_H$ is the mass a
Hydrogen's atom, $\tau$  the optical depth, $\sigma$ is the cross
section at the line's center and $n$ is the number density of neutral
Hydrogen atoms. 
For this system we estimate that for average values of $n=1\times
10^3$ the total hydrogen mass is $M\times 10^{14}$M$_{\odot}$. 
However, blind HI
surveys have put an upper limit in the neutral hydrogen mass of ???
